\documentclass[10pt]{article}

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[a4paper, margin=1cm]{geometry}

\pagenumbering{gobble}

\begin{document}
	\noindent\textbf{\LARGE Izaac Mammadov \Large JP }\\
	Address: 292 White Hart Lane \hfill Email: \href{mailto:izaac@mammadov.co.uk}{izaac@mammadov.co.uk}\\
	\phantom{Address: }London, N17 8JP \hfill Website: \href{https://izaac.mammadov.co.uk}{izaac.mammadov.co.uk}\\
	Mobile: +44 7825308878 \hfill GitHub: \href{https://github.com/IzaacMammadov}{IzaacMammadov}
	\rule{\textwidth}{0.5pt}\\[0.1cm]
	\textsc{\Large Education}
	\begin{itemize}[left=0pt]
		\item \textbf{\href{https://www.corpus.cam.ac.uk/}{Corpus Christi College}, \href{https://www.cam.ac.uk/}{University of Cambridge} \hfill Cambridge, UK}\\
		\textit{B.A. (Hons) Mathematical Tripos [Mathematics] \hfill October 2019--June 2022}
		\begin{itemize}
			\item High 1st Class, scoring 84\% and ranked 18th out of $\sim$250 students.
			\item Awarded two scholarships for academic excellence, including the Richard Metheringham prize by the Worshipful Company of Cutlers.
		\end{itemize}
		\item \textbf{\href{https://www.latymer.co.uk/}{The Latymer School} \hfill London, UK}\\
		\textit{A Levels in Mathematics, Further Mathematics, Physics and Chemistry \hfill September 2012--June 2019}
		\begin{itemize}
			\item A*A*A*A* (A Level), SSS (STEP Mathematics), Silver Medal in British Mathematics Olympiad (top 50).
		\end{itemize}
	\end{itemize}
	\rule{\textwidth}{0.5pt}\\[0.1cm]
	\textsc{\Large Work Experience}
	\begin{itemize}[left=0pt]
		\item \textbf{\href{https://gattaca.com/}{Gattaca} \hfill {London, UK}}\\
		\textit{Software Engineer \hfill November 2025--Current}
		\begin{itemize}
			\item \textbf{Low-latency Development}: Developed low-latency infrastructure in \texttt{Rust} as part of ``TitanBuilder'' (block-builder on \texttt{Ethereum} mainnet with the largest market-share) and ``TitanRelay'' (a popular \texttt{Ethereum} relay to connect validators and block-builders).
			\item \textbf{Alt-Chains}: Worked on \texttt{Solana} block-building and validator execution scheduling.
		\end{itemize}
		\item \textbf{\href{https://www.find-court-tribunal.service.gov.uk/courts/highbury-corner-magistrates-court}{Highbury Corner Magistrates Court} \hfill London, UK}\\
		\textit{Magistrate Judge / Justice of the Peace (JP) \hfill May 2025--Current}
		\begin{itemize}
			\item \textbf{Magistrate}: Volunteer Judge, adjudicating summary and either-way criminal cases and sentencing defendants.
		\end{itemize}
		\item \textbf{\href{https://www.quarrylp.com/}{The Quarry LP} \hfill Remote}\\
		\textit{Quantitative Researcher \hfill January 2024--November 2025}
		\begin{itemize}
			\item \textbf{Strategy Creation}: Created and improved on quantitative strategies based on Bayesian machine-learning techniques, with a focus on trading equity volatililty.
			\item \textbf{Strategy Backtesting}: Backtested medium-frequency quantitative strategies and created reports outlining their
			profit metrics and analysis on their hyperparameters.
			\item \textbf{Portfolio Optimisation}: Created interactive pages to display results surrounding optimal portfolio allocation and
			calculating mean-variance efficient portfolios, as well as sandboxes for visualising different portfolio weightings.
			\item \textbf{Derivatives Pricing}: Developed systems for pricing a variety of vanilla and exotic derivatives and calculating their respective greeks for the purposes of backtesting and execution.
		\end{itemize} 
		\item \textbf{\href{https://wintermute.com/}{Wintermute Trading} \hfill London, UK}\\
		\textit{Algorithmic Trader \hfill July 2022--December 2023}
		\begin{itemize}
			\item \textbf{Market-Making}: Refined high-frequency market-making strategies which traded dozens of cryptocurrencies across multiple exchanges, as well as automated the setting of parameters for those strategies using A-B testing.
			\item \textbf{Exchange Integration}: Integrated centralised cryptocurrency exchanges’ endpoints (Order Entry, Order Feed etc.) using WebSockets, REST and
			FIX protocols. 
		\end{itemize}
		\item \textbf{\href{https://www.flowtraders.com/}{Flow Traders} \hfill Amsterdam, The Netherlands}\\
		\textit{Trading Intern \hfill June 2021--August 2021}
	\end{itemize}
	\rule{\textwidth}{0.5pt}\\[0.1cm]
	\textsc{\Large Interests and Skills}
	\begin{itemize}[left=0pt]
		\item \textbf{Programming}: Proficient in \texttt{Python} (including \texttt{aiohttp}, \texttt{matplotlib}, \texttt{numpy}, \texttt{pandas}, \texttt{scikit-learn} and \texttt{scipy}), \texttt{C++} (including the \texttt{boost} libraries) and \texttt{Rust} (including \texttt{tokio}). Experienced in managing \texttt{PostgreSQL} and \texttt{MongoDB} databases and \texttt{AWS} infrastructure (\texttt{EC2}, \texttt{S3}, \texttt{RDS}).
		\item \textbf{Projects}: Currently run my own self-hosted website, build with static site generator \texttt{Hugo} and served by \texttt{NGINX}, as well as my own email server and mailbox using \texttt{Dovecot} and \texttt{Postfix}. I also run my own self-hosted \texttt{Urbit} star. 
		\item \textbf{Foreign Languages}: Raised in a bilingual household speaking English and Russian as well as Azerbaijani.
		\item \textbf{Interests}: Promoting Free and Open-Source software use and helping people maintain their privacy. Cryptography and Crypto CTF (Capture The Flag) competitions.
	\end{itemize}
\end{document}